Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-08-08 volunteer-clouds-ieee-ci-si.tex
JS and plugin vulnerabilities

The main problem with Java and all the other browser-embedded
technologies is that they are not {\em universal} in the
sense than an extra component, namely, the Java virtual machine, has
to be installed in the browser. JavaScript, however,
\cite{flanagan2006javascript} was introduced in 1997 as a
browser-embedded language and has, since then, become a set of standards
\cite{ECMA-262} that include the language and its components. Since
early on, it was adopted by the industry and also by scientists,
who used them for creating an EA on
the browser as early as 1998 \cite{jj-ppsn98}.

@@

Recent works propose the use of cloud computing services for the components of 
client-server distributed EAs. Cloud resources 
can reduce operational costs by outsourcing both hardware and software maintenance 
to the cloud provider. Another advantage is that they enable the provisioning of computing resources beyond what 
is available in most laboratories, allowing researches to 
scale algorithms at reasonable costs. Researchers have proposed the use of 
public clouds such as Amazon EC2 \cite{CloudScale}, Google App Engine\cite{di2013towards} 
and DropBox~\cite{mericloud}. The use of JavaScript to implement
server side components 
gives software developers certain advantages in the cloud
paradigm, since is a first-classe citizen 
in most Platforms as a Service (PaaS) products as most support the Node.js
framework \cite{wood13:nodejs:paas}. Many web services  
have native JavaScript libraries too, and use JSON (JavaScript Object Notation) for data
interchange. Another advantage is that  
developers can use the same software tools for both client and server
side development.
%Ayuda con la mini conclusion FERGU: mira la última frase de arriba
% Borrada por iterativa - JJ

@@

In the work presented in this paper, JavaScript has been used throughout the full 
stack, which has the advantage of using the self-same lines of code for
writing an evolutionary algorithm for the
desktop or command line and browser clients, both based in the EC
library NodEO \cite{DBLP:conf/gecco/GuervosVGES14}. This saves time
when writing code and leverages %FERGU: qué diferencias hay entre NodIO y NodEO??
expertise acquired in the library itself. %FERGU: tienes info de LoC
                                %usadas para la sección experimental y
                                %justificar esta frase?
% Es el mismo código - JJ
%The proposed software has the advantage of full stack JavaScript
%development..
% Ya se ha dicho, ¿no? - JJ

@@

%Mario: Estaba pensando que otra justificación muy fuerte para el uso de JS sobre plug-ins 
%ha sido la seguridad ya que estos presentan otra fuente de vulnerabilidad. Para complicar las cosas a veces (Flash, ActiveX) 
%son tecnologías cerradas y propietarias. Por lo menos creo que esas
%fueron las razones que se dieron para eliminar a Flash del iPhone.
% [JJ] Escribe algo...

@@

%El último párrafo podría ser más preciso. Es el único experimento que utiliza recursos heterogeneos
%empleando las tecnologías estándar (JavaScript, JSON, Cookies, etc.) mencionadas previamente.

%Si no se extiende mucho se podría también hablar de la conexión con Cloud Computing,
%se discuten las ventajas de utilizar JavaScript para acceder a recursos donados por voluntarios
%pero falta hablar de como se explotaría el recurso Cloud. Lo digo por el titulo de Volunteers in the Clouds. Tal vez
%se deba hablar de la posibilidad de escalar los sistemas a bajo costo
%o según la demanda.
% Ya se ha hablado. Revísalo - JJ

% Si te animas, propón un párrafo - JJ
% Ok, lo escribo. - Mario
% Voy escribiendo algo de HTML5 y Web Workers?, no necesariemente para
% esta sección. 
% Para la intro o esta sección - JJ

@@

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different web technologies, such as JQuery or chart.js have
been used to build the elements of the system. 
%FERGU: Mario, explica en el texto de abajo qué es winston en la figura también. 
%Vamos, que todo lo que salga en la figura tiene que ir en el texto en alguna parte :)
% [Mario] Ok voy a explicar la figura. Quería saber primero su opinión tal vez se les hacía mucho detalle.
% Creo que esta figura va mejor en la sección donde hablamos de
% webworkers. La anterior era más adecuada como visión general. [JJ]
\begin{figure}[!t]
\centering
\includegraphics[width=4in]{img/system.pdf}
\caption{Description of the proposed system. Clients execute a JS EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one from the server. }  
\label{fig:system}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=12cm]{img/baseline-times.png}
\caption{Comparison of time to solution for the baseline system, using a {\tt
    node.js} client, for different population sizes. They only compare on
runs in which solution has been found.}
\label{fig:baseline}
\end{figure}
First we establish the baseline performance by running the
evolutionary algorithm in a desktop client written using NodEO, 
%FERGU: es NodEO o NodIO? Quito el \sf, por cierto, que queda feo
%Por qué usamos NodEO aquí y no NodIO, vamos a compararlos? 
%Qué diferencias hay entre los dos? (ponerlo en el SOA)
%[Mario] Creo que es NodEO y NodIO fué mi error.
the node.js evolutionary algorithm library. This experiment tries to 
%FERGU: quitar el "the node.js evolutionary algorithm library", si ya lo hemos dicho
%o explicarlo mejor: "the basic js library we have used as base to built NodIO", por ejemplo
find the solution to the 40-trap function with parameters $l=4, a=1,
b=2, z=3$, a population size equal 512. The algorithm was run until the solution (a string with all
ones) was found or five millions evaluations had been performed. It
took around a minute, on average, that is $68.9694$ seconds, to
perform the fifty runs. In this experiment only 33, that is, 66\% were
successful. The experiments were repeated for population $p=1024$,
with success rate upgraded to 100\% and average duration $3.46$
seconds. Results for these two experiments 
are shown in Figure \ref{fig:baseline}.

>>>>

The main problem with Java and all the other browser-embedded
technologies is that they are not {\em universal} in the
sense than an extra component, namely, the Java virtual machine or another
virtual environment has to be installed in the browser. 
Also these virtual environments have become targets of malicious attacks; % [Mario] Aqui empieza 
for instance numerous vulnerabilities have been discovered in % lo que decía de la seguridad.
the propietary Adobe Flash runtime environment and 
video player \cite{ford2009analyzing,watanabe2010new}. The need for
these additional environments has been mitigated with the 
adoption of the HTML5 standard \cite{anthes2012html5}.
JavaScript, however,
\cite{flanagan2006javascript} was introduced in 1997 as a
browser-embedded language and has, since then, become a set of standards
\cite{ECMA-262} that include the language and its components. Since
early on, it was adopted by the industry and also by scientists,
who used them for creating an EA on
the browser as early as 1998 \cite{jj-ppsn98}.

@@

Recent works propose the use of cloud computing services for the components of 
client-server distributed EAs. Cloud resources 
can reduce operational costs by outsourcing both hardware and software maintenance 
to the cloud provider. Another advantage is that they enable the provisioning of computing resources beyond what 
is available in most laboratories, allowing researches to 
scale algorithms at reasonable costs. Researchers have proposed the use of 
public clouds such as Amazon EC2 \cite{CloudScale}, Google App Engine\cite{di2013towards} 
and DropBox~\cite{mericloud}. The use of JavaScript to implement
server side components 
gives software developers certain advantages in the cloud
paradigm, since is a first-classe citizen 
in most Platforms as a Service (PaaS) products as most support the Node.js
framework \cite{wood13:nodejs:paas}. Many web services  
have native JavaScript libraries too, and use JSON (JavaScript Object Notation) for data
interchange. Another advantage is that  
developers can use the same software tools for both client and server
side development.
% Ayuda con la mini conclusion FERGU: mira la última frase de arriba
% Borrada por iterativa - JJ

@@

In the work presented in this paper, JavaScript has been used throughout the full 
stack, which has the advantage of using the self-same lines of code for
writing an evolutionary algorithm for the
desktop or command line and browser clients, both based in the EC
library NodEO \cite{DBLP:conf/gecco/GuervosVGES14}. This saves time % [Mario] Creo que si se debería
% dedicar una oración para recordar la diferencia y relación entre NodIO y NodEO
% En mi mente los digo igual, NodEO como Rodeo y NodIO como Radio y me costó trabajo ver la diferencia
% Pero igual un lector que llegue a leer sin vicios, si vea claramente la relación. 
when writing code and leverages %FERGU: qué diferencias hay entre NodIO y NodEO??
expertise acquired in the library itself. %FERGU: tienes info de LoC
                                %usadas para la sección experimental y
                                %justificar esta frase?
% Es el mismo código - JJ
%The proposed software has the advantage of full stack JavaScript
%development..
% Ya se ha dicho, ¿no? - JJ 
% Si, eso ya quedó - Mario

@@

%Mario: Estaba pensando que otra justificación muy fuerte para el uso de JS sobre plug-ins 
%ha sido la seguridad ya que estos presentan otra fuente de vulnerabilidad. Para complicar las cosas a veces (Flash, ActiveX) 
%son tecnologías cerradas y propietarias. Por lo menos creo que esas
%fueron las razones que se dieron para eliminar a Flash del iPhone.
% [JJ] Escribe algo... 
% [Mario] Ok, aunque va unos párrafos antes.

@@

%El último párrafo podría ser más preciso. Es el único experimento que utiliza recursos heterogeneos
%empleando las tecnologías estándar (JavaScript, JSON, Cookies, etc.) mencionadas previamente.
%[Mario] Ya quedó esto

%Si no se extiende mucho se podría también hablar de la conexión con Cloud Computing,
%se discuten las ventajas de utilizar JavaScript para acceder a recursos donados por voluntarios
%pero falta hablar de como se explotaría el recurso Cloud. Lo digo por el titulo de Volunteers in the Clouds. Tal vez
%se deba hablar de la posibilidad de escalar los sistemas a bajo costo
%o según la demanda.
% Ya se ha hablado. Revísalo - JJ
% Si, ya quedó -Mario

% Si te animas, propón un párrafo - JJ
% Ok, lo escribo. - Mario
% Voy escribiendo algo de HTML5 y Web Workers?, no necesariemente para
% esta sección. 
% Para la intro o esta sección - JJ
% Ya se hizo - Mario

@@

Figure \ref{fig:system} describes the general system architecture and
algorithm behavior. Different web technologies, such as JQuery or chart.js have
been used to build the elements of the system. 
%FERGU: Mario, explica en el texto de abajo qué es winston en la figura también. 
%Vamos, que todo lo que salga en la figura tiene que ir en el texto en alguna parte :)
% [Mario] Ok voy a explicar la figura. Quería saber primero su opinión tal vez se les hacía mucho detalle.
% Creo que esta figura va mejor en la sección donde hablamos de
% webworkers. La anterior era más adecuada como visión general. [JJ]
% [Mario] Ok
\begin{figure}[!t]
\centering
\includegraphics[width=4in]{img/system.pdf}
\caption{Description of the proposed system. Clients execute a JS EA
  in the browser, which, every 100 generations, sends the best
  individual and receives a random one from the server. }  
\label{fig:system}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=12cm]{img/baseline-times.png}
\caption{Comparison of time to solution for the baseline system, using a {\tt
    node.js} client, for different population sizes. They only compare on
runs in which solution has been found.}
\label{fig:baseline}
\end{figure}
First we establish the baseline performance by running the
evolutionary algorithm in a desktop client written using NodEO, 
%FERGU: es NodEO o NodIO? Quito el \sf, por cierto, que queda feo
%Por qué usamos NodEO aquí y no NodIO, vamos a compararlos? 
%Qué diferencias hay entre los dos? (ponerlo en el SOA)
%[Mario] Creo que es NodEO y NodIO fué mi error. 
%[Mario] Ok, ya me quedó claro. Pero no sé si quede claro en el paper, sin leer el otro.
the node.js evolutionary algorithm library. This experiment tries to 
%FERGU: quitar el "the node.js evolutionary algorithm library", si ya lo hemos dicho
%o explicarlo mejor: "the basic js library we have used as base to built NodIO", por ejemplo
find the solution to the 40-trap function with parameters $l=4, a=1,
b=2, z=3$, a population size equal 512. The algorithm was run until the solution (a string with all
ones) was found or five millions evaluations had been performed. It
took around a minute, on average, that is $68.9694$ seconds, to
perform the fifty runs. In this experiment only 33, that is, 66\% were
successful. The experiments were repeated for population $p=1024$,
with success rate upgraded to 100\% and average duration $3.46$
seconds. Results for these two experiments 
are shown in Figure \ref{fig:baseline}.
